\begin{itemize}
  \item Kurniawan, A. (2021). Introduction to NVIDIA Jetson Nano. In: IoT Projects with NVIDIA Jetson Nano. Apress, Berkeley, CA.
  \item Nvidia Jetson \url{https://en.wikipedia.org/wiki/Nvidia_Jetson#cite_note-8}
  \item Jetson Nano \url{https://www.nvidia.com/es-la/autonomous-machines/embedded-systems/jetson-nano/product-development/}
  \item ¿Qué puedo hacer con una Jetson Nano? \url{https://www.330ohms.com/blogs/blog/que-puedo-hacer-con-una-jetson-nano }
  \item Mistral Solutions. (2024, 31 julio). Mistral Blog | NIVIDIA Jetson Applications - NVIDIA Jetson Nano, NVIDIA Jetson TX2 NX, NVIDIA Jetson Xavier NX. \url{https://www.mistralsolutions.com/blog/nvidia-jetson-modules-use-cases-part-2/#:~:text=Jetson%20Nano%20is%20ideal%20for,image%20recognition%2C%20and%20object%20counting.}
  \item Vision alerting system with IoT Edge, Azure Custom Vision and Jetson. (s. f.). NVIDIA Developer. \url{https://developer.nvidia.com/embedded/community/jetson-projects/vision_alerting_system}
  \item AI for Healthcare with Jetson Nano 2GB. (s. f.). NVIDIA Developer. \url{https://developer.nvidia.com/embedded/community/jetson-projects/ai_for_healthcare}
  \item amazon.com: NVIDIA Jetson Nano Developer Kit : Electronics. (2024). Amazon.com. \url{https://www.amazon.com/NVIDIA-Jetson-Nano-Developer-Kit/dp/B07PZHBDKT%E2%80%8C}
  \item amazon.com: Jetson Nano 4GB RAM 16G eMMC integrado para AI Robotics Machine Learning (versión disipador de calor) : Electrónica. (2024). Amazon.com. \url{https://www.amazon.com/-/es/integrado-Robotics-Machine-Learning-disipador/dp/B0B8DMPWJL/ref=pb_allspark_dp_sims_pao_desktop_session_based_d_sccl_2_3/142-2880780-0925111?psc=1%E2%80%8C}
\end{itemize}